Report on Certificate Tools

### 2016-08-31 TEX/draft.tex
Added more text to Keytool

>>>>

      \paragraph{Self-signed certificate}
To generate new key pair and self-signed certificate use:
\begin{verbatim}
keytool -genkey -keyalg [RSA|DSA] -alias [alisaname] \
        -keystore [keystore_file] -storepass [password] \
        -validity [time] -keysize [length]
\end{verbatim}

Keytool natively supports only DSA of length in between 512 and 1024, and is considered to be dangerous to use. RSA with key length of at least 2048 is preffered.

      \paragraph{Certificate Signing Request}
To generate a Certificate Signing Request generation of a key pair with alias is needed:
\begin{verbatim}
keytool -genkey -alias namealias -keyalg [RSA|DSA] \
        –keysize [length] -keystore [keystore_path | new_keystore_name]
\end{verbatim}
To create a CSR you then need to do:
\begin{verbatim}
keytool -certreq -keyalg [keyalg_from_genkey] -alias [alias_from_genkey] -file certreq.csr -keystore [jks_from_genkey]
\end{verbatim}
Where you need to set -keyalg -alias and -keystore as chosen when generating key pair earlier.
      \paragraph{Specify length}
Length is specified when generating keys, RSA support for up to 4096, DSA support from 512 up to 1024.

      \paragraph{Specify algorithm}
Algorithm is specified while generating key pair, currently support for DSA, RSA. EC is needed to be implemented.      
    \subsubsection{Basic constraints}
